The National Eutrophication Survey: lake characteristics and historical nutrient concentrations

### 2017-11-07 08_manuscript/template.tex
add tables

\Author[1]{Joseph}{Stachelek}
\Author[2]{Chanse}{Ford}
\Author[3]{Dustin}{Kincaid}
\Author[1]{Katelyn}{King}
\Author[4]{Heather}{Miller}
\Author[5]{Nagelkirk}{Ryan}

@@

% insert table 1

@@

% insert table 2

>>>>

\Author[1]{Joseph}{Stachelek}
\Author[2]{Chanse}{Ford}
\Author[3]{Dustin}{Kincaid}
\Author[1]{Katelyn}{King}
\Author[4]{Heather}{Miller}
\Author[5]{Ryan}{Nagelkirk}

@@

\begin{table*}
\caption{Number of measurements (n) for each variable in each NES region.}
\begin{tabular}{lllll}
\tophline
Variable & Western & Central & Northeastern & Southeastern\\
\middlehline
Drainage area & 122 & 138 & 171 & 232\\
\hline
Surface area & 152 & 177 & 200 & 245\\

Mean depth & 149 & 174 & 174 & 242\\

Total inflow & 124 & 138 & 170 & 232\\

Retention time & 124 & 140 & 158 & 230\\

Alkalinity & 153 & 177 & 200 & 245\\

Conductivity & 153 & 176 & 200 & 245\\

Secchi depth & 153 & 177 & 200 & 245\\

Total P & 153 & 177 & 200 & 245\\

Total inorg. P & 153 & 177 & 200 & 245\\

Total inorg. N & 153 & 177 & 200 & 245\\

Total N & 152 & 176 & 1 & 245\\

P pt. source mun. & 52 & 83 & 139 & 189\\

P pt. source ind. & 7 & 1 & 10 & 24\\

P pt. source sep. & 65 & 88 & 111 & 175\\

P nonpt. source & 122 & 133 & 167 & 231\\

P total inputs & 122 & 133 & 167 & 231\\

N pt. source mun. & 52 & 84 & 139 & 189\\

N pt. source ind. & 7 & 1 & 8 & 22\\

N pt. source sep. & 77 & 90 & 111 & 184\\

N nonpt. source & 122 & 129 & 167 & 231\\

N total inputs & 122 & 129 & 167 & 231\\

P total exports & 119 & 132 & 167 & 227\\

P retention & 99 & 115 & 144 & 201\\

P load per area & 122 & 133 & 167 & 231\\

N total exports & 119 & 133 & 166 & 227\\

N retention & 88 & 111 & 122 & 170\\

N load per area & 122 & 135 & 167 & 231\\
\bottomhline
\end{tabular}
\end{table*}

%\begin{table*}[t]
%\caption{TEXT}
%\begin{tabular}{column = lcr}
%\tophline
%
%\middlehline
%
%\bottomhline
%\end{tabular}
%\belowtable{} % Table Footnotes
%\end{table*}

@@

\begin{table*}[t]
\caption{Mean and standard deviation (sd) for each variable in each NES region.}
\begin{tabular}{lllllllllllll}
\tophline
\multicolumn{1}{l|}{Region} & \multicolumn{3}{|c|}{Western} & \multicolumn{3}{|c|}{Central} & \multicolumn{3}{|c|}{Northeastern} & \multicolumn{3}{|c}{Southeastern} \\ \cline{1-1} \cline{2-4} \cline{5-7} \cline{8-10} \cline{11-13}
Variable & Mean &   & sd & Mean &   & sd & Mean &   & sd & Mean &   & sd\\
\middlehline
Drainage area ($km^{2}$) & 2.5e+04 & ± & 7.8e+04 & 2.1e+04 & ± & 7.5e+04 & 3.2e+03 & ± & 1.4e+04 & 5.3e+03 & ± & 1.4e+04\\

Surface area ($km^{2}$) & 44.57 & ± & 99.83 & 54.38 & ± & 1.4e+02 & 27.25 & ± & 99.01 & 42.7 & ± & 1.4e+02\\

Mean depth ($m$) & 16.71 & ± & 27.08 & 5.97 & ± & 4.49 & 7 & ± & 9.37 & 6.4 & ± & 6.07\\

Total inflow ($m^{3} \cdot s^{-1}$) & 52.1 & ± & 1.1e+02 & 31.82 & ± & 71.77 & 23.1 & ± & 65.26 & 82.6 & ± & 2.3e+02\\

Retention time ($years$) & 7.27 & ± & 43.32 & 2.78 & ± & 6.98 & 2.01 & ± & 4.77 & 0.59 & ± & 1.12\\

Alkalinity ($mg \cdot l^{-1}$) & 1.7e+02 & ± & 3.7e+02 & 1.5e+02 & ± & 91.51 & 1.2e+02 & ± & 1.6e+02 & 72.18 & ± & 66.25\\

Conductivity ($uohm$) & 4.9e+02 & ± & 1.0e+03 & 6.4e+02 & ± & 7.6e+02 & 3.3e+02 & ± & 4.0e+02 & 2.5e+02 & ± & 2.2e+02\\

Secchi depth ($m$) & 2.86 & ± & 2.64 & 1.2 & ± & 0.91 & 1.81 & ± & 1.71 & 1.22 & ± & 0.82\\

Total P ($mg \cdot l^{-1}$) & 0.07 & ± & 0.13 & 0.11 & ± & 0.16 & 0.16 & ± & 0.35 & 0.12 & ± & 0.27\\

Total inorg. P ($mg \cdot l^{-1}$) & 0.04 & ± & 0.11 & 0.04 & ± & 0.07 & 0.11 & ± & 0.3 & 0.05 & ± & 0.15\\

Total inorg. N ($mg \cdot l^{-1}$) & 0.14 & ± & 0.23 & 0.33 & ± & 0.58 & 0.47 & ± & 0.66 & 0.72 & ± & 0.91\\

Total N ($mg \cdot l^{-1}$) & 0.62 & ± & 0.65 & 1.22 & ± & 1.11 & 0.12 & ± & NA & 1.56 & ± & 1.25\\

P pt. source mun. ($kg \cdot yr^{-1}$) & 2.5e+04 & ± & 8.7e+04 & 2.3e+04 & ± & 5.6e+04 & 3.5e+04 & ± & 1.5e+05 & 4.5e+04 & ± & 1.1e+05\\

P pt. source ind. ($kg \cdot yr^{-1}$) & 2.5e+04 & ± & 4.0e+04 & 1.3e+04 & ± & NA & 2.7e+04 & ± & 4.9e+04 & 1.7e+04 & ± & 4.5e+04\\

P pt. source sep. ($kg \cdot yr^{-1}$) & 56.62 & ± & 1.4e+02 & 60.62 & ± & 93.67 & 1.6e+02 & ± & 3.4e+02 & 98.55 & ± & 2.3e+02\\

P nonpt. source ($kg \cdot yr^{-1}$) & 1.4e+05 & ± & 4.2e+05 & 1.8e+05 & ± & 6.8e+05 & 5.6e+04 & ± & 2.1e+05 & 1.9e+05 & ± & 5.5e+05\\

P total inputs ($kg \cdot yr^{-1}$) & 1.5e+05 & ± & 4.7e+05 & 2.0e+05 & ± & 7.0e+05 & 8.7e+04 & ± & 3.4e+05 & 2.3e+05 & ± & 5.8e+05\\

N pt. source mun. ($kg \cdot yr^{-1}$) & 7.8e+04 & ± & 2.5e+05 & 7.3e+04 & ± & 1.7e+05 & 1.4e+05 & ± & 5.4e+05 & 1.4e+05 & ± & 3.8e+05\\

N pt. source ind. ($kg \cdot yr^{-1}$) & 2.3e+07 & ± & 6.1e+07 & 4.0e+03 & ± & NA & 1.6e+05 & ± & 4.2e+05 & 1.7e+05 & ± & 5.6e+05\\

N pt. source sep. ($kg \cdot yr^{-1}$) & 5.7e+06 & ± & 5.0e+07 & 2.2e+03 & ± & 3.5e+03 & 4.3e+03 & ± & 5.5e+03 & 3.3e+03 & ± & 6.7e+03\\

N nonpt. source ($kg \cdot yr^{-1}$) & 1.8e+06 & ± & 4.9e+06 & 1.8e+06 & ± & 4.4e+06 & 1.2e+06 & ± & 4.1e+06 & 3.1e+06 & ± & 8.9e+06\\

N total inputs ($kg \cdot yr^{-1}$) & 6.8e+06 & ± & 5.7e+07 & 1.8e+06 & ± & 4.3e+06 & 1.3e+06 & ± & 4.6e+06 & 3.2e+06 & ± & 9.0e+06\\

P total exports ($kg \cdot yr^{-1}$) & 6.2e+04 & ± & 1.7e+05 & 7.4e+04 & ± & 1.9e+05 & 7.3e+04 & ± & 3.1e+05 & 1.9e+05 & ± & 6.3e+05\\

P retention (\%) & 47.77 & ± & 28.5 & 57.55 & ± & 26.01 & 36.93 & ± & 25.2 & 42.7 & ± & 23.34\\

P load per area($g / m^{2} / day$) & 5.61 & ± & 21.36 & 3.3 & ± & 9.2 & 28.46 & ± & 97.49 & 9.43 & ± & 17.06\\

N total exports ($kg \cdot yr^{-1}$) & 1.6e+06 & ± & 4.0e+06 & 1.2e+06 & ± & 2.8e+06 & 1.2e+06 & ± & 4.9e+06 & 3.0e+06 & ± & 8.3e+06\\

N retention (\%) & 39.33 & ± & 27.13 & 43.41 & ± & 23.97 & 28.41 & ± & 23.62 & 26.28 & ± & 18.85\\

N load per area ($g / m^{2} / day$) & 1.8e+02 & ± & 1.1e+03 & 42.67 & ± & 1.1e+02 & 2.8e+02 & ± & 9.1e+02 & 1.3e+02 & ± & 2.4e+02\\
\bottomhline
\end{tabular}
\end{table*}
